### 2014-11-13 model.tex
Fixes

In this section, we describe the system model and introduce the primitive
relations that our contract language is seeded with. Figure~\ref{fig:sysmod}
provides a schematic diagram of our system model. The distributed store is
composed of a collection of \emph{replicas}, each of which stores a set of
\emph{objects} ($x,y,\ldots$). We assume that every object is replicated at
every replica in the store. The state of an object at any replica is the set of
all updates (\emph{effects}) performed on the object. For example, the state of
$x$ at replica 1 is the ordered set composed of effects $w^x_1$ and $w^x_2$.

>>>>

In this section, we describe the system model and introduce the primitive
relations that our contract language is seeded with. Figure~\ref{fig:sysmod}
presents a schematic diagram of our system model. The distributed store is
composed of a collection of \emph{replicas}, each of which stores a set of
\emph{objects} ($x,y,\ldots$). We assume that every object is replicated at
every replica in the store. The state of an object at any replica is the set of
all updates (\emph{effects}) performed on the object. For example, the state of
$x$ at replica 1 is the set composed of effects $w^x_1$ and $w^x_2$.
